\author{Anthony Odenthal - KE7OSN}
\title{W7PRA Meeting Monday November 19th 2018 19:00}
\documentclass[letter,11pt]{extarticle}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\setlist{noitemsep}
\usepackage{color}
\usepackage{array}
\usepackage{hyperref}
\usepackage[compact]{titlesec}
\usepackage{listings}
\titlespacing*{\section}{0pt}{6pt}{6pt}
\titlespacing*{\subsection}{0pt}{6pt}{6pt}

\begin{document}
	\thispagestyle{empty}
	
	\begin{center}
		\textbf{W7PRA\\Meeting Agenda}
		\vspace{0.33cm}
	\end{center}
	
	\begin{center}
		\begin{tabular}{| m{3.0cm} | m{7.5cm} |} \hline
			\textbf{Date and Time} & Monday 19\textsuperscript{th} November 2018 at 19:00 \\ \hline
			\textbf{Venue} & Tommy's 4\textsuperscript{th} Street Bar \& Grill \\ \hline
				\end{tabular}
	\end{center}
	
	\begin{center}
		\textbf{Please pay your bill by 8pm}
	\end{center}
	
	\subsection*{Agenda}
	\begin{enumerate}
		\item Call to Order
		\item Introductions
		\item Secretary's Report - Ted
		\item Treasurer's Report - Andy \\
				Balances 
			\begin{tabular}{|l|l|} \hline
				OSUCU Checking & \$1,061.14 \\ \hline
				OSUCU Savings & \$1,579.90 \\ \hline
				Paypal & \$46.00 \\ \hline
				Square & \$0.00 \\ \hline
				Cash & \$49.22.00 \\ \hline
				\textbf{Total} & \textbf{\$2,736.31} \\ \hline
			\end{tabular} \\ \\
%			Expenses
%			\begin{description}
%				\item[Donation to AB7BS] \$500.00
%			\end{description}
		\item Trustee's Report - Mike
			\begin{itemize}
				\item 440.725+ DCS 023 Roxy Ann Peak - Medford
				\item 441.325+ DCS 023 Coburg Rdige Eugene
				\item 449.475 Horsetooth Mtn - Albany
			\end{itemize}
		\item Bunny Hunt on hiatus - Mike
		\item Previous Events/Old Business:
		\begin{itemize}
			\item Swaptoberfest - October 20\textsuperscript{th} Polk County Fairgrounds
			\item ARRL Elections - Results
				\begin{description}
					\item[Director] Mike Ritz W7VO
					\item[Vice Director] Mark Tharp KB7HDX
				\end{description}
		\end{itemize}
			
		\item  New Business / Upcoming Events
			\begin{itemize}
				\item  Christmas Meeting - December 17\textsuperscript{th}. We will have a very limited business meeting, with our primary focus on a social gathering and white elephant gift exchange. Feel free to bring spouses, SO's, children. All are welcome.
				\item White Elephant Gift Exchange - Anyone is welcome to take part. but in order for it to work everyone that is needs to bring a gift. To take part, bring a wrapped, unmarked gift. We tend towards a radio related theme. There will be a table to place them on. We will count the number of gifts and put those numbers in a hat, and everyone who brought a gift will get to draw a number. In order each person will have the option to either open a gift from the table, or to steal a gift that has already been opened. Once a gift has been stolen twice (third person to ''own'' it) it is locked and can not be stolen any more. If your gift is stolen you may then steal another gift or open a new one. A gift may not change hands more than once per round. At the very end the person with \#1 has the option to ''trade'' the gift they currently have with any other non-locked gift in the room. Normally the value of the gifts range from \$25-50, radios, speakers, tuners, etc. have been popular. We have also seen Clocks, Raspberry $\pi$'s and ''refreshments''. 
			\end{itemize}
		\item Recap of the last month in Radio
			\begin{itemize}
				\item Solar Activity
				\item DX
				\item Achievements?
			\end{itemize}
		\item  Presentation - Mike
	\end{enumerate}

%\newpage

	Current Officers \\
	\begin{tabular}{|l|l|} \hline
		Chair & Anthony Odenthal KE7OSN \\ \hline
		Secretary & Ted Mitchell W7RTM \\ \hline
		Treasurer & Andy Prentice W7AAU \\ \hline
		Trustee & Mike Shelby W7RIS   \\ \hline
		Board & Bill Powell KE7ZKH \\ \hline
		Board & Matt Cawrse KF7DVN \\ \hline
		Board & Drew Terrill W3HES\\ \hline
	\end{tabular}
	
	\subsection*{\color{red}{Next Meeting: Monday 17\textsuperscript{th} December 2018 at 19:00.}}
	
\end{document}
